% budget, talk about affordability for the consumers, and also mention that this SD project is funded out of pocket, and the choices for budget were made with these interests in mind.
\subsection{Economic Contraints}
\noindent One of the main constraints for our project FORWARD is economic constraints. Our project is self-funded, which means that we can spend as little or as much as we wanted, but given the current state of our teams financial situation, this was limited to \$250 to \$400. We also needed to conserve 10\% to 20\% of our budget for back up components and extra PCB boards. Due to this, our already limited budget is now cut down even more, which will in turn, limit the quality and efficiency of the components we can afford. \\

\noindent Due to the high cost of AI hardware, selecting the chip/MCU that will run the object detection models was one of our main constraints. Much of the GPU hardware is far to expensive and out of scope for this project, leaving us to look into the current state of AI focused embedded MCU hardware. Many of the preexisting products implement hardware that can cost anywhere from \$250 to \$500, which is well outside of our budget - in fact, some of which would consume our entire budget. In order to work within this constraint, we were able to find a low cost MCU driven camera board which had a MCU capable of running light weight AI models. The downside to this board is a lower camera quality, which could make certain stretch requirements such as depth perception more difficult. It also limits the quality of the object detection models that we can run. \\

\noindent The motor system was also part of the economic constraints for our project. The motor drivers/shield board and the motors for similar applications (i.e electric scooters, vacuum cleaners, other walkers) can cost upwards to around \$50 each. To limit the cost of such, we needed to implement a walker solution with only two motors (front wheel drive). The limitation decrease the control we can have over the walker as well as will cause for faster deterioration of the front wheels over time. \\

\noindent Another aspect of our projects economic constraints is the power system. Our system runs on 21.6 V and many of the power supply's can cost upwards to \$70 each for our purposes. For this aspect of the project, there isn't much we can due to avoid this cost, which means we must spend extra time in research for the part we will use, and everything else will be limited as an effect. \\

\noindent Overall, the constraints listed above can be very limiting for our project and create possible issues later on. In an effort to avoid this, we are taking extra precaution to maximize our budget through extensive research. We can also always extend our budget later on, but that is undesired. \\