\begin{thebibliography}{45}
	
	% seminal UCF work
	\bibitem{Mostofa} Mostofa N, Feltner C, Fullin K, Guilbe J, Zehtabian S, Bacanlı SS, Bölöni L, Turgut D. A Smart Walker for People with Both Visual and Mobility Impairment. Sensors. 2021; 21(10):3488. https://doi.org/10.3390/s21103488
	
	% seminal work all-time
	\bibitem{PAMM} S. Dubowsky et al., "PAMM - a robotic aid to the elderly for mobility assistance and monitoring: a "helping-hand" for the elderly," Proceedings 2000 ICRA. Millennium Conference. IEEE International Conference on Robotics and Automation. Symposia Proceedings (Cat. No.00CH37065), San Francisco, CA, USA, 2000, pp. 570-576 vol.1, doi: 10.1109/ROBOT.2000.844114.ex
	
	% sensor fusion fall detection
	\bibitem{FallDetect} D. -M. Ding, Y. -G. Wang, W. Zhang and Q. Chen, "Fall Detection System on Smart Walker Based on Multisensor Data Fusion and SPRT Method," in IEEE Access, vol. 10, pp. 80932-80948, 2022, doi: 10.1109/ACCESS.2022.3195674.
	
	% lidar smart walker
	\bibitem{mstate} T. Dirheimer, J. Hancock, D. Hill, Y. Kochubievsky, and S. Moore, Smart Walker Design: Final Report, ECE 480, Michigan State University, April 29, 2015.
	
	% sonar vs lidar
	\bibitem{sonarvslidar} "Laser vs Ultrasonic Distance Sensor Tests," DroneBot Workshop, Sep. 29, 2019. [Online]. Available: https://dronebotworkshop.com/laser-vs-ultrasonic-distance-sensor-tests/. [Accessed: Sep. 10, 2024].

	% how brakes work
	\bibitem{Brain} Brain, M. (n.d.). How brakes work. HowStuffWorks. https://auto.howstuffworks.com/auto-parts/brakes/brake-types/brake.htm
	
	% finding how long a battery will last - calculator
	\bibitem{Calculator Academy} Calculator Academy. (n.d.). Battery run time calculator. Calculator Academy. https://calculator.academy/battery-run-time-calculator/ 
	
	% market analysis
	\bibitem{Grand View Research} Grand View Research. (2024). Assisted walking devices market size, share \& trends analysis report by product type (Canes, Crutches, Walkers, Gait Trainers), by region, and segment forecasts, 2022 - 2030. Grand View Research. https://www.grandviewresearch.com/industry-analysis/assisted-walking-device-market
	
	% what bicycle lights are required by law
	\bibitem{Perez} Mallard Perez. (n.d.). What the Florida law says about bicycle lights. Mallard Perez. https://www.mallardperez.com/faqs/what-the-florida-law-says-about-bicycle-lights.cfm 
	
\end{thebibliography}