\begin{thebibliography}{45}
	
	% seminal UCF work
	\bibitem{Mostofa} Mostofa N, Feltner C, Fullin K, Guilbe J, Zehtabian S, Bacanlı SS, Bölöni L, Turgut D. A Smart Walker for People with Both Visual and Mobility Impairment. Sensors. 2021; 21(10):3488. \href{https://doi.org/10.3390/s21103488}{https://doi.org/10.3390/s21103488}
	
	% seminal work all-time
	\bibitem{PAMM} S. Dubowsky et al., "PAMM - a robotic aid to the elderly for mobility assistance and monitoring: a 'helping-hand' for the elderly," Proceedings 2000 ICRA. Millennium Conference. IEEE International Conference on Robotics and Automation. Symposia Proceedings (Cat. No.00CH37065), San Francisco, CA, USA, 2000, pp. 570-576 vol.1, \href{https://doi.org/10.1109/ROBOT.2000.844114}{doi:10.1109/ROBOT.2000.844114}
	
	% object detection AI/ML GNC application paper for VIPs
	\bibitem{CVRef1} B. K. Asiedu Asante and H. Imamura, "Towards Robust Obstacle Avoidance for the Visually Impaired Person Using Stereo Cameras," Technologies, vol. 11, no. 6, p. 168, 2023. \href{https://doi.org/10.3390/technologies11060168}{doi:10.3390/technologies11060168}
	
	% Lightweight model focused project
	\bibitem{CVRef2} A. B. Atitallah, Y. Said, M. A. B. Atitallah, M. Albekairi, K. Kaaniche, and S. Boubaker, "An effective obstacle detection system using deep learning advantages to aid blind and visually impaired navigation," Ain Shams Engineering Journal, vol. 15, no. 2, p. 102387, 2024. \href{https://doi.org/10.1016/j.asej.2023.102387}{doi:10.1016/j.asej.2023.102387}
	
	% ESP32 BLE environmental sensing project example
	\bibitem{bluetoothSensorProject} Rui Santos, "ESP32 BLE Server – Environmental Sensing Service (ESP-IDF)," Random Nerd Tutorials, 6 October 2022. [Online]. Available: \href{https://randomnerdtutorials.com/esp32-ble-server-environmental-sensing-service/}{https://randomnerdtutorials.com/esp32-ble-server-environmental-sensing-service/}. [Accessed: Oct. 29, 2024].

	% ESP32 camera module project ref
	\bibitem{ESP32CamRef1} How2Electronics, "ESP32-CAM based object detection \& identification with OpenCV," How2Electronics. [Online]. Available: \href{https://how2electronics.com/esp32-cam-based-object-detection-identification-with-opencv/}{https://how2electronics.com/esp32-cam-based-object-detection-identification-with-opencv/}. [Accessed: Oct. 9, 2024].
	
	% RealTek Camera Project Ref
	\bibitem{RealTekCamRef1} How To Electronics, "Object Detection \& Identification with AMB82 Mini AI Camera," How2Electronics. Available: \href{https://how2electronics.com/object-detection-identification-with-amb82-mini-ai-camera/}{https://how2electronics.com/object-detection-identification-with-amb82-mini-ai-camera/}. [Accessed: Oct. 9, 2024].
	
	\bibitem{HowYOLOWorks} R. Kumar, "YOLO Object Detection Explained," DataCamp, https://www.datacamp.com/blog/yolo-object-detection-explained. (accessed Oct. 24, 2024).
	
	% Bone conduction ref article
	\bibitem{BoneConductionRef} Soundscape HQ, "Unlock Sound Through Bones: Understanding Bone Conduction," \emph{Soundscape HQ}, 2024. [Online]. Available: \href{https://soundscapehq.com/what-is-bone-conduction/}{https://soundscapehq.com/what-is-bone-conduction/}. [Accessed: Oct. 15, 2024].

	\bibitem{bluetooth} Bluetooth Technology, "Tech Overview," Bluetooth.com, https://www.bluetooth.com/learn-about-bluetooth/tech-overview/. (accessed Oct. 24, 2024).
	
	\bibitem{bluetoothHow} C. Woodford, "How Bluetooth Works," Explain That Stuff, https://www.explainthatstuff.com/howbluetoothworks.html. (accessed Oct. 24, 2024).

	% Amazon Bone Conduction Ear Pieces
	\bibitem{BoneConductEar1} YouthWhisper Bone Conduction Headphones Bluetooth, Wireless Open-Ear Headset with Microphones, Titanium Lightweight Sweat Resistant, Answer Phone Sports Earphones for Running Hiking Bicycling Black \href{https://www.walmart.com/ip/YouthWhisper-Bone-Conduction-Headphones-Bluetooth-Wireless-Open-Ear-Headset-Microphones-Titanium-Lightweight-Sweat-Resistant-Answer-Phone-Sports-Earp/278825770?clickid=WjORv5UqyxyKRJqTvVUblVgLUkCRR\%3AxQe1ri}{https://www.walmart.com/ip/YouthWhisper-Bone-Conduction-Headphones-Bluetooth-Wireless-Open-Ear-Headset-Microphones-Titanium-Lightweight-Sweat-Resistant-Answer-Phone-Sports-Earp/278825770}
	
	% Amazon ambient sound earbuds
	\bibitem{AmbientSoundEarbuds} JLab Wireless Bluetooth Charging Multipoint Earbuds, Ambient Sound Mode. \href{https://www.amazon.com/JLab-Wireless-Bluetooth-Charging-Multipoint/dp/B0CC772D37}{https://www.amazon.com/JLab-Wireless-Bluetooth-Charging-Multipoint/dp/B0CC772D37}
	
	% sensor fusion fall detection
	\bibitem{FallDetect} D. -M. Ding, Y. -G. Wang, W. Zhang and Q. Chen, "Fall Detection System on Smart Walker Based on Multisensor Data Fusion and SPRT Method," in IEEE Access, vol. 10, pp. 80932-80948, 2022. \href{https://doi.org/10.1109/ACCESS.2022.3195674}{doi:10.1109/ACCESS.2022.3195674}
	
	% lidar smart walker
	\bibitem{mstate} T. Dirheimer, J. Hancock, D. Hill, Y. Kochubievsky, and S. Moore, Smart Walker Design: Final Report, ECE 480, Michigan State University, April 29, 2015.
	
	\bibitem{lidar-type} ThinkAutonomous. “Types of LiDAR: What's the difference? | Think Autonomous,” ThinkAutonomous.ai, [Online]. Available: \href{https://www.thinkautonomous.ai/blog/types-of-lidar/}{https://www.thinkautonomous.ai/blog/types-of-lidar/}. Accessed: Sep. 15, 2024.
	
	\bibitem{sonar-type} M. Toa and A. Whitehead, "Ultrasonic Sensing Basics," Texas Instruments, Application Report SLAA907D, Dec. 2021. [Online]. Available: \href{https://www.ti.com/lit/an/slaa907d/slaa907d.pdf}{https://www.ti.com/lit/an/slaa907d/slaa907d.pdf}. Accessed: Sep. 15, 2024.
	
	% sonar vs lidar
	\bibitem{sonar-vs-lidar} "Laser vs Ultrasonic Distance Sensor Tests," DroneBot Workshop, Sep. 29, 2019. [Online]. Available: \href{https://dronebotworkshop.com/laser-vs-ultrasonic-distance-sensor-tests/}{https://dronebotworkshop.com/laser-vs-ultrasonic-distance-sensor-tests/}. [Accessed: Sep. 10, 2024].
	
	% camera vs. lidar/ultrasonic
	\bibitem{camera-vs-sensor} "Pros and cons of camera, LiDAR, RADAR, and ultrasonic detection technologies in AV," \textit{ResearchGate}. [Online]. Available: \href{https://www.researchgate.net/figure/Pros-and-cons-of-camera-LiDAR-RADAR-and-ultrasonic-detection-technologies-in-AV\_tbl}{https://www.researchgate.net/figure/Pros-and-cons-of-camera-LiDAR-RADAR-and-ultrasonic-detection-technologies-in-AV\_tbl}. [Accessed: Sep. 15, 2024].
	
	% ultrasonic directivity figure
	\bibitem{coolUltraDirect} Microsonic, "Detection Zones," Microsonic, [Online]. Available: \href{https://www.microsonic.de/en/support/ultrasonic-technology/detection-zones.htm}{https://www.microsonic.de/en/support/ultrasonic-technology/detection-zones.htm}. [Accessed: 15-Sep-2024].
	
	% lidar FOV figure
	\bibitem{coolLiDARfov} R. M. [Last Name], "FOV Definition: Optical axis of scanning LIDAR (Black dotted line)," ResearchGate, [Online]. Available: \href{https://www.researchgate.net/figure/FOV-Definition-Optical-axis-of-scanning-LIDAR-Black-dotted-line\_fig1\_280132809}{https://www.researchgate.net/figure/FOV-Definition-Optical-axis-of-scanning-LIDAR-Black-dotted-line\_fig1\_280132809}. [Accessed: 15-Sep-2024].
	
	% walker with stretch requirements: stability and curb lifter
	\bibitem{byACRE} byACRE, "Carbon Ultralight Rollator," byACRE, [Online]. Available: \href{https://shop.byacre.com/us/carbon-ultralight-rollator.html}{https://shop.byacre.com/us/carbon-ultralight-rollator.html}. [Accessed: 16-Sep-2024].
	
	% walker with mechanical speed control (not electronic) and curb lifting
	\bibitem{ustep} uStep, "Standard Model," uStep, Available: \href{https://www.ustep.com/product/standard-model}{https://www.ustep.com/product/standard-model}.
	
	% quaternions
	\bibitem{quat} E. W. Weisstein, "Quaternion," MathWorld--A Wolfram Web Resource. [Online]. Available: \href{https://mathworld.wolfram.com/Quaternion.html.}{https://mathworld.wolfram.com/Quaternion.html.}.
	
	% seminal Kalman filter paper
	\bibitem{kalman} R. E. Kalman, "A new approach to linear filtering and prediction problems," Journal of Basic Engineering, vol. 82, no. 1, pp. 35-45, Mar. 1960. [Online]. Available: \href{https://www.cs.unc.edu/~welch/kalman/media/pdf/Kalman1960.pdf}{https://www.cs.unc.edu/~welch/kalman/media/pdf/Kalman1960.pdf}.
	
	% how brakes work
	\bibitem{Brain} Brain, M. (n.d.). How brakes work. HowStuffWorks. \href{https://auto.howstuffworks.com/auto-parts/brakes/brake-types/brake.htm}{https://auto.howstuffworks.com/auto-parts/brakes/brake-types/brake.htm}
	
	% finding how long a battery will last - calculator
	\bibitem{Calculator Academy} Calculator Academy. (n.d.). Battery run time calculator. Calculator Academy. \href{https://calculator.academy/battery-run-time-calculator/}{https://calculator.academy/battery-run-time-calculator/}
	
	% market analysis
	\bibitem{Grand View Research} Grand View Research. (2024). Assisted walking devices market size, share \& trends analysis report by product type (Canes, Crutches, Walkers, Gait Trainers), by region, and segment forecasts, 2022 - 2030. Grand View Research. \href{https://www.grandviewresearch.com/industry-analysis/assisted-walking-device-market}{https://www.grandviewresearch.com/industry-analysis/assisted-walking-device-market}
	
	% what bicycle lights are required by law
	\bibitem{Perez} Mallard Perez. (n.d.). What the Florida law says about bicycle lights. Mallard Perez. \href{https://www.mallardperez.com/faqs/what-the-florida-law-says-about-bicycle-lights.cfm}{https://www.mallardperez.com/faqs/what-the-florida-law-says-about-bicycle-lights.cfm}.
	
	\bibitem{apollo} Apollo Scooters, "Understanding Electric Scooter Controllers," Apollo Scooters, [Online]. Available: \href{https://apolloscooters.co/blogs/news/understanding-electric-scooter-controllers?srsltid=AfmBOoqWTbV4qa2VxA8NxpdquVzQMn4LeQYiwBG756xhscX0vExgNW-8}{https://apolloscooters.co/blogs/news/understanding-electric-scooter-controllers}. [Accessed: Oct. 24, 2024].
	
	\bibitem{hwang2020} J. S. Hwang, S. Y. Kim, and H. M. Kim, "A Study on the Design of the Control Algorithm for the Electric Scooter," \textit{IEEE Access}, vol. 8, pp. 146207-146215, 2020. \href{https://ieeexplore.ieee.org/document/9137951}{https://ieeexplore.ieee.org/document/9137951}. [Accessed: Oct. 24, 2024].

	\bibitem{coreelectronics} Core Electronics, "Motor Drivers vs. Motor Controllers," Core Electronics, [Online]. Available: \href{https://core-electronics.com.au/guides/motor-drivers-vs-motor-controllers/}{https://core-electronics.com.au/guides/motor-drivers-vs-motor-controllers/}. [Accessed: Oct. 24, 2024].
	
	\bibitem{thingbits} Thingbits, "Motor Drivers," Thingbits, [Online]. Available: \href{https://www.thingbits.in/t/categories/motors-and-drivers/motor-drivers}{https://www.thingbits.in/t/categories/motors-and-drivers/motor-drivers}. [Accessed: Oct. 24, 2024].
	
	\bibitem{powerelectronics} Power Electronics News, "Learning the Basics of Motor Control," Power Electronics News, [Online]. Available: \href{https://www.powerelectronicsnews.com/learning-the-basics-of-motor-control/}{https://www.powerelectronicsnews.com/learning-the-basics-of-motor-control/}. [Accessed: Oct. 24, 2024].
	
	\bibitem{etechsparks} Etech Sparks, "DC Motor Controller: Working Principle \& Definition," Etech Sparks, [Online]. Available: \href{https://etechsparks.com/dc-motor-controller-working-principle-definition/}{https://etechsparks.com/dc-motor-controller-working-principle-definition/}. [Accessed: Oct. 24, 2024].
	
	\bibitem{elprocus1} Elprocus, "Different Types of Electric Motors," Elprocus, [Online]. Available: \url{https://www.elprocus.com/different-types-of-electric-motors/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{pihut} The Pi Hut, "What's the Difference Between DC, Servo \& Stepper Motors?" The Pi Hut, [Online]. Available: \url{https://thepihut.com/blogs/raspberry-pi-tutorials/whats-the-difference-between-dc-servo-amp-stepper-motors}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{powerelectric} Power Electric, "AC Motors vs. DC Motors," Power Electric, [Online]. Available: \url{https://www.powerelectric.com/motor-blog/ac-motors-vs-dc-motors}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{elprocus2} Elprocus, "DC Motor: Basics, Types, and Applications," Elprocus, [Online]. Available: \url{https://www.elprocus.com/dc-motor-basics-types-application/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{elprocus3} Elprocus, "DC Shunt Motor: Construction, Working Principle, and Circuit Diagram," Elprocus, [Online]. Available: \url{https://www.elprocus.com/dc-shunt-motor-construction-working-principle-circuit-diagram/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{elprocus4} Elprocus, "DC Series Motor: Components, Circuit Diagram, and Applications," Elprocus, [Online]. Available: \url{https://www.elprocus.com/dc-series-motor-components-circuit-diagram-applications/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{elprocus5} Elprocus, "PMDC (Permanent Magnetic DC) Motor: Construction and Working," Elprocus, [Online]. Available: \url{https://www.elprocus.com/pmdc-permanent-magnetic-dc-motor-construction-working/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{linquip} Linquip, "Compound DC Motors," Linquip, [Online]. Available: \url{https://www.linquip.com/blog/compound-dc-motors/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{elprocus6} Elprocus, "Brushless DC Motor: Advantages, Applications, and Control," Elprocus, [Online]. Available: \url{https://www.elprocus.com/brushless-dc-motor-advantages-applications-and-control/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{monolithicpower} Monolithic Power Systems, "Brushless vs. Brushed DC Motors," Monolithic Power Systems, [Online]. Available: \url{https://www.monolithicpower.com/en/learning/resources/brushless-vs-brushed-dc-motors}. [Accessed: Oct. 24, 2024].
	
	\bibitem{spikevm} 
	Spike VM, "RPM to MPH Calculator," Spike VM, [Online]. Available: \url{https://www.spikevm.com/calculators/fuel_distance/rpm-mph.php}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{lee2019} 
	J. Lee, J. Kim, and H. Kim, "A Study on the Efficiency of Electric Motors," \textit{Nat. Sci. Rep.}, vol. 9, no. 1, pp. 1-11, 2019. [Online]. Available: \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6353162/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{trionic} 
	Trionic, "How Much Weight Can the Rollator Hold," Trionic, [Online]. Available: \url{https://www.trionic.us/en/knowledge/135/how-much-weight-can-the-rollator-hold}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{gribble} 
	Gribble, "Cycling Power vs. Speed Calculator," Gribble, [Online]. Available: \url{https://www.gribble.org/cycling/power_v_speed.html?units=metric&rp_wr=74.843&rp_wb=17&rp_a=0.509&rp_cd=0.63&rp_dtl=1&ep_crr=0.04&ep_rho=1.22601&ep_g=8&ep_headwind=0&p2v=200&v2p=35.41}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{drive} 
	Drive Medical, "Drive Medical Rollator with Removable Back Support," Amazon, [Online]. Available: \url{https://www.amazon.com/Drive-Medical-Rollator-Removable-Support/dp/B00NFJX0PU}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{xconvert} 
	XConvert, "Square Inches to Square Feet Converter," XConvert, [Online]. Available: \url{https://www.xconvert.com/unit-converter/square-inches-to-square-feet}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{oxwheels} 
	Ox Wheels, "Does Tyre Size Affect Car Performance?" Ox Wheels, [Online]. Available: \url{https://www.oxwheels.com.au/Does-tyre-size-affect-car-performance}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{ebikesforum} 
	E-Bikes Forum, "Does a 750 Front and a 750 Rear Add Up to 1500 Watts?" E-Bikes Forum, [Online]. Available: \url{https://ebikesforum.com/threads/does-a-750-front-and-a-750-rear-add-up-to-1500-watts.5464/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{yzl1} 
	YZL, "150W Brushless DC Motor Replacement Cylindrical 13000-15000RPM," Amazon, [Online]. Available: \url{https://www.amazon.com/Brushless-Cylindrical-13000-15000RPM-Propulsion-Specific/dp/B09NCJ24W6}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Citphto} 
	Citphto, "775 6000-12000RPM Electric Brushless Motor," Amazon. [Online]. Available: \url{https://www.amazon.com/Citphto-775-6000-12000RPM-Electric-Electrical/dp/B0CMXM1N94}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress1} 
	AliExpress, "Electric Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256807288642417.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress2} 
	AliExpress, "Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256804436743610.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress3} 
	AliExpress, "DC Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256802991206296.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress4} 
	AliExpress, "High Torque Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256807195926102.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{UMLIFE} 
	UMLIFE, "300W Three Phase Brushless Motor Controller," Amazon. [Online]. Available: \url{https://www.amazon.com/UMLIFE-Three-Phase-Brushless-Controller-Control/dp/B09BHXLGW6}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Burgess} 
	C. Burgess, "Quad Motor Servo Shield for ESP32 Project Board," Tindie. [Online]. Available: \url{https://www.tindie.com/products/cburgess129/quad-motor-servo-shield-for-esp32-project-board/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Espressif1} 
	Espressif Systems, "ESP32-WROOM-32 Datasheet," Espressif. [Online]. Available: \url{https://www.espressif.com/sites/default/files/documentation/esp32-wroom-32_datasheet_en.pdf}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{RandomNerd} 
	Random Nerd Tutorials, "Installing the ESP32 Board in Arduino IDE (Windows Instructions)," Random Nerd Tutorials. [Online]. Available: \url{https://randomnerdtutorials.com/installing-the-esp32-board-in-arduino-ide-windows-instructions/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Espressif2} 
	Espressif Systems, "MCPWM API Reference," Espressif. [Online]. Available: \url{https://docs.espressif.com/projects/esp-idf/en/v4.4.2/esp32/api-reference/peripherals/mcpwm.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Peza} 
	P. Peza, "TB6612FNG\_ESP32," GitHub. [Online]. Available: \url{https://github.com/pablopeza/TB6612FNG_ESP32}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{SimpleFOC} 
	SimpleFOC, "Installation Guide," SimpleFOC. [Online]. Available: \url{https://docs.simplefoc.com/installation}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress5} 
	AliExpress, "DC Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256805324882671.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Makerbase} 
	Makerbase Motor, "MKS ESP32 FOC V1.0 Manual," GitHub. [Online]. Available: \url{https://github.com/makerbase-motor/MKS-ESP32FOC/blob/master/User%20Manual/MKS%20ESP32%20FOC%20V1.0%20Manual.pdf}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{ActPower} 
	Act Power, "What Is a Power Supply and How Does It Work?" Act Power. [Online]. Available: \url{https://www.actpower.com/blog/what-is-a-power-supply-and-how-does-it-work/}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{RCBeacon} 
	RC Beacon, "Power Supply Units (PSUs): General Information," RC Beacon. [Online]. Available: \url{https://rcbeacon.com/pmb/psu_general_1.htm}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{PrecisionMicrodrives} 
	Precision Microdrives, "AB-001: Discrete Driver Circuits for Vibration Motors," Precision Microdrives. [Online]. Available: \url{https://www.precisionmicrodrives.com/ab-001-discrete-driver-circuits-for-vibration-motors}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress6} 
	AliExpress, "High Torque Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256803905606674.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{StackExchange} 
	Stack Exchange, "What is the safe amount of current I can apply to a DC motor?" Stack Exchange. [Online]. Available: \url{https://electronics.stackexchange.com/questions/301233/what-is-the-safe-amount-of-current-i-can-apply-to-a-dc-motor}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{ArduinoForum} 
	Arduino Forum, "Stall Current vs. Rated Current," Arduino Forum. [Online]. Available: \url{https://forum.arduino.cc/t/stall-current-vs-rated-current/1004977}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress7} 
	AliExpress, "High-Speed Brushless Motor," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256805089628613.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{CircuitBasics} 
	Circuit Basics, "SRD-05VDC-SL-C Relay Datasheet," Circuit Basics. [Online]. Available: \url{https://www.circuitbasics.com/wp-content/uploads/2015/11/SRD-05VDC-SL-C-Datasheet.pdf}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{AliExpress8} 
	AliExpress, "Brushless Motor Controller," AliExpress. [Online]. Available: \url{https://www.aliexpress.us/item/3256806182053704.html}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{SimpleFOC2} 
	SimpleFOC, "Supported Microcontrollers," SimpleFOC. [Online]. Available: \url{https://docs.simplefoc.com/microcontrollers}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{HiLetgo} 
	HiLetgo, "DRV8871 H-Bridge Motor Driver Breakout Board," Amazon. [Online]. Available: \url{https://www.amazon.com/HiLetgo-DRV8871-H-Bridge-Breakout-6-5V-45V/dp/B0CDWW7FZ8}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Hobbywing} 
	"Hobbywing QuicRun 1060 Brushed ESC," Amazon. [Online]. Available: \url{https://www.amazon.com/dp/B00F839VNQ}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{BOJACK} 
	BOJACK, "DC Motor Speed Controller, Adjustable Voltage Regulator," Amazon. [Online]. Available: \url{https://www.amazon.com/BOJACK-Voltage-Controller-Adjustable-Driver/dp/B09P6D5TMV}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{Gikfun} 
	"Gikfun L298N Dual H Bridge Motor Driver," Amazon. [Online]. Available: \url{https://www.amazon.com/gp/product/B09HXXG3DM}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{BEEYDC} 
	"BEEYDC 12V 24V 36V 48V DC Motor Speed Controller," Amazon. [Online]. Available: \url{https://www.amazon.com/gp/product/B0CR6BX5QL}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{RioRand} 
	RioRand, "DC Motor Controller, High Efficiency, Reversible, with Overcurrent Protection," Amazon. [Online]. Available: \url{https://www.amazon.com/RioRand-Controller-Efficiency-Generating-Protection/dp/B007TH4EN6}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{uxcell} 
	"uxcell 5V Vibration Motor, Electric Vibrating Massager," Amazon. [Online]. Available: \url{https://www.amazon.com/uxcell-Vibration-Vibrating-Electric-Massager/dp/B08265KJLY}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{DIANN} 
	DIANN, "Vibration Button Type Switch, 10mm x 2.7mm," Amazon. [Online]. Available: \url{https://www.amazon.com/DIANN-Vibration-Button-Type-10mmx2-7mm-Appliances/dp/B0B4SK8M1C}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{eBayDC} 
	"Electric DC Motor 12V 550," eBay. [Online]. Available: \url{https://www.ebay.com/itm/125600353141}. [Accessed: Oct. 24, 2024]. 
	
	\bibitem{INeedMotors} 
	"How to Match Battery with Motor," I Need Motors. [Online]. Available: \url{https://www.ineedmotors.com/news/how-to-match-battery-with-motor-69783315.html}. [Accessed: Oct. 24, 2024]
	
	\bibitem{oxford_health_2014} 
	
	Oxford Health NHS Foundation Trust, ``Safety information leaflet: four-wheeled rollators,'' 2014. [Online]. Available: \url{https://www.oxfordhealth.nhs.uk/wp-content/uploads/2014/08/OP-101.15-Safety-information-leaflet-four-wheeled-rollators.pdf}. [Accessed: Oct. 28, 2024].
		 
	\bibitem{nfpmotor}
	NFPMotor, ``Vibrating Vibrator Vibration Motors,'' \textit{NFPMotor}, [Online]. Available: \url{https://www.nfpmotor.com/Vibrating-vibrator-vibration-motors.html#:~:text=Haptics%20Motor%20-%20by%20the%20definition,through%20the%20use%20of%20vibrations}. [Accessed: 7-Nov-2024].
	
	\bibitem{geeksforgeeks_voltage_regulation}
	GeeksforGeeks, ``Voltage Regulation,'' \textit{GeeksforGeeks}, [Online]. Available: \url{https://www.geeksforgeeks.org/voltage-regulation/}. [Accessed: 7-Nov-2024].
	
	\bibitem{vogely2024}
	Vogely, \textit{Vogely Universal 12V Electric Headlight for Bike, Motorcycle, Waterproof}, Amazon, [Online]. Available: \url{https://www.amazon.com/Vogely-Universal-Headlight-Electric-Waterproof/dp/B0CHKP8899}. [Accessed: Nov. 12, 2024].
	
	\bibitem{frdhee2024}
	Frdhee, \textit{Frdhee Motorcycle LED Headlight, High Brightness Conversion, Waterproof}, Amazon, [Online]. Available: \url{https://www.amazon.com/Frdhee-Motorcycle-Brightness-Headlights-Conversion/dp/B0DGQD1DXF/ref=sr_1_23?crid=2TBUAGBXRIDAA&dib=eyJ2IjoiMSJ9.Bw0hUngN_FfXnbyiQmIjag9aXvRcQFYMiMTow34zag4NBh8VQS8BZaf3-UQFMqJoK3aamzn4C57wci8yY7IQfqiuNMkg0gMnpWlbW8_hA9MmaFPauWfw9xndDkhS0sD_ggo6-ab_3LFlQRN4_UQTGV_z2C_Rw8Bqr_ZxJwnENlyS6PgU4heHzIAQtoADL91fZnKFP-4Xe2IlOjaCwKMLCN_XHR9gdTbBi-e-tnIRWYhKFivX5PiulPRAJ8zCc-7IEMR2Tc9w9c_p9-VMTMCLUITbqk_BVBtnSOwzbr2c9zk.Jj7GE6TTNpy0wI9oH1BiHZ9zulinaG8pXcY5n13zmBA&dib_tag=se&keywords=electric%2Bheadlight&qid=1731384528&sprefix=electric%2Bheadlight%2Caps%2C174&sr=8-23&th=1&psc=1}. [Accessed: Nov. 12, 2024].
	
	\bibitem{stellarlights2024}
	StellarLights, \textit{StellarLights 1600 Lumen LED Bicycle Headlight, Wide-Angle Beam, Waterproof}, Amazon, [Online]. Available: \url{https://www.amazon.com/StellarLights-Lumen-Bicycle-Headlight-Wide-Angle/dp/B019E81TMQ/ref=sr_1_87?crid=SI26K5INHEXE&dib=eyJ2IjoiMSJ9.cqbZnnB2T83LvSKMugRXgkCScs4XZvBSRQrTcKrPa2_xFRcY61JRfXKEV0SpM-1g2BJpvtquHGCTYiH0oCgQRtDhDYq5xFpaeD1vqb0taZD2oSPqyrJDYdTbF4AwymYNSxnL6qjYQA9z-ynJvWfMAZGRUQmR7tIYYkEa7U8mzeygcFTZ-R_Svz7VbI_-WMTunymyCZQEgeyn7X4lB_0EriQTwhLzY_YDT4h-yyoJLx3xo3bAaGRERdkcORArGZxuZJqVAN7hQ0jF_xMR6WpaRXkdDpmLv0Lkge7z3v-aoEI.Qb_wRFvKZ2dMDIrIF7m76dWFgSyvk1VCvZUErT8qVAw&dib_tag=se&keywords=bike%2Bheadlight&qid=1731383790&refinements=p_36%3A-1200&rnid=386589011&sprefix=bike%2Bheadlight%2Caps%2C271&sr=8-87&th=1}. [Accessed: Nov. 12, 2024].
	
	\bibitem{analog2024}
	Analog Devices, \textit{Light Sensor Glossary}, [Online]. Available: \url{https://www.analog.com/en/resources/glossary/light-sensor.html#:~:text=Common%20types%20of%20light%20sensors,proximity%20sensors%2C%20and%20renewable%20energy}. [Accessed: Nov. 12, 2024].
	
	\bibitem{eepower2024}
	EE Power, \textit{Photoresistor Guide}, [Online]. Available: \url{https://eepower.com/resistor-guide/resistor-types/photo-resistor/#}. [Accessed: Nov. 12, 2024].
	
	\bibitem{byjus2024}
	Byju's, \textit{Photodiodes and Their Applications}, [Online]. Available: \url{https://byjus.com/physics/photodiodes-applications/#:~:text=Photodiodes%20are%20used%20in%20safety,used%20in%20solar%20cell%20panels}. [Accessed: Nov. 12, 2024].
	
	\bibitem{globalspec2024}
	GlobalSpec, \textit{Phototransistors and Their Applications}, [Online]. Available: \url{https://www.globalspec.com/learnmore/optics_optical_components/optoelectronics/phototransistors#:~:text=Phototransistors%20are%20used%20in%20almost,are%20more%20sensitive%20than%20photodiodes}. [Accessed: Nov. 12, 2024].
	
	\bibitem{ub12452024}
	UB1245, \textit{UB1245 SLA1250 12V 4.5AH Sealed Lead Acid (SLA) Battery for Medical Devices}, Amazon, [Online]. Available: \url{https://www.amazon.com/UB1245-SLA1250-Battery-12V4-5AH-Medical/dp/B0B2F8VQW2/ref=sr_1_25?crid=3PMYZZNW7UKXA&dib=eyJ2IjoiMSJ9.X8csgQtFQoACxgT9yTB45Z5_XNgff2P3aeaAebGcw8z6P4-eN0V3XgAgzRNe8sjImjrQMCnsyOOitfNrBdQ4dOqunFwFGExxoD6Keq5f32Ctu5iO9LtFRhc9QSSmY4adE5HgScgzmSk9esykk4Dut9A0taypEPj8F0oKwGab64NaiWQj21gQAH4bI3vOaOCVjNG-0wn2skCFL3HnAO47uXX_LtXiYj6E42m874N9g2zgNdwRqCrPQmlQBhHv-j3EXFC6j7rqQ5rHqF9iKJ2YpELkjaW_gzTP3vquUVh-pSs.posU3ZC8nx8_nnF1_bOzplxkdYj9tW-yGgYzC0uSfLg&dib_tag=se&keywords=12v+5ah+battery&qid=1731528204&refinements=p_36%3A-2000&rnid=386636011&sprefix=12v+5ah+battery%2Caps%2C156&sr=8-25}. [Accessed: Nov. 12, 2024].
	
	\bibitem{liftmaster2024}
	LiftMaster, \textit{LiftMaster 485LM Replacement Battery by SigmasTek for Garage Door Openers}, Amazon, [Online]. Available: \url{https://www.amazon.com/Liftmaster-485LM-Replacement-Battery-SigmasTek/dp/B07DLBQMTG/ref=sr_1_37?crid=3PMYZZNW7UKXA&dib=eyJ2IjoiMSJ9.X8csgQtFQoACxgT9yTB45Z5_XNgff2P3aeaAebGcw8z6P4-eN0V3XgAgzRNe8sjImjrQMCnsyOOitfNrBdQ4dOqunFwFGExxoD6Keq5f32Ctu5iO9LtFRhc9QSSmY4adE5HgScgzmSk9esykk4Dut9A0taypEPj8F0oKwGab64NaiWQj21gQAH4bI3vOaOCVjNG-0wn2skCFL3HnAO47uXX_LtXiYj6E42m874N9g2zgNdwRqCrPQmlQBhHv-j3EXFC6j7rqQ5rHqF9iKJ2YpELkjaW_gzTP3vquUVh-pSs.posU3ZC8nx8_nnF1_bOzplxkdYj9tW-yGgYzC0uSfLg&dib_tag=se&keywords=12v+5ah+battery&qid=1731528204&refinements=p_36%3A-2000&rnid=386636011&sprefix=12v+5ah+battery%2Caps%2C156&sr=8-37}. [Accessed: Nov. 12, 2024].
	
	\bibitem{lifepo42024}
	NewtiPower, \textit{LiFePO4 12V 6Ah Lithium Iron Phosphate Battery for Overland Applications}, Amazon, [Online]. Available: \url{https://www.amazon.com/LiFePO4-NewtiPower-Phosphate-Overland-Applications/dp/B0CLKGZTVL/ref=sr_1_18?crid=1DAII15KD4DBK&dib=eyJ2IjoiMSJ9.T3TrHc9NiW58k6jEHCpoMKuKZCcqC0YPbQCeu4rFfpkq9r1p2srjiWz770ljal6fi8BDZdNschSdNbp9xQYyCZm9YH6_Ax58Px5rVydRHi-kwz4femr4vV9081Fk3v-NpF1KgH0EOJh5WLUWHatXKhHJEZrmQbGzt06DcUlYOZlzSqJKiBOlOWq0FNUhCZYE6aMT1RpZJd1zJg01zIJBV9UZj63-AzJgL5bbJcMheP1X5ig-n3ktH9qLPIz5kcvoGOHsN-zorrj3zUflI55p83M13lEo8vKaTg2LKzCT_IU.9ylGtRMVS9G6wKECoMuzAZHcPO4XTQGrIza42Jt-WVg&dib_tag=se&keywords=12v+6ah+battery&qid=1731529264&refinements=p_36%3A-2700&rnid=386419011&sprefix=12v+ah+battery%2Caps%2C177&sr=8-18}. [Accessed: Nov. 12, 2024].
	
	\bibitem{electricaleasy2014} ElectricalEasy, "Electric Braking of DC Motors," 2014. [Online]. Available: \url{https://www.electricaleasy.com/2014/01/electric-braking-of-dc-motors.html#:~:text=Braking%20effect%20is%20controlled%20by,rheostat%20is%20connected%20in%20series}. [Accessed: Nov. 16, 2024]. 
	
	\bibitem{bayalarm2024} Bay Alarm, "How Do Motion Sensors Work? A Guide," 2024. [Online]. Available: \url{https://www.bayalarm.com/blog/how-do-motion-sensors-work-a-guide/#:~:text=A%20motion%20sensor%2C%20or%20motion,right%20to%20your%20mobile%20phone}. [Accessed: Nov. 16, 2024]. 
	
	\bibitem{amazon12024}
	Amazon, "550 30000RPM Gearbox with 12V Motor for Power Wheels, RS550 12 Volt DC Motor High Speed Match Children Powered Ride On Car," [Online]. Available: \url{https://www.amazon.com/dp/B072F7QWBQ?ref=ppx_yo2ov_dt_b_fed_asin_title}. [Accessed: Nov. 16, 2024].
	
	\bibitem{lucidar2024}
	Lucidar, "Revolution Per Minute to Miles Per Hour Converter," [Online]. Available: \url{https://lucidar.me/en/unit-converter/revolution-per-minute-to-miles-per-hour/}. [Accessed: Nov. 16, 2024].
	
	\bibitem{sparkfun12024}
	SparkFun, "ESP32 Thing Hookup Guide - Hardware Overview," [Online]. Available: \url{https://learn.sparkfun.com/tutorials/esp32-thing-hookup-guide/hardware-overview#:~:text=The%20ESP32's%20operating%20voltage%20range,pins%20are%20not%205V%2Dtolerant!}. [Accessed: Nov. 16, 2024].
	
\end{thebibliography}
